Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2017-02-07 manuscript/main.tex
addressed point asking about further discusion of inverse frequency weighting

In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency--inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results). This measure is different and potentially preferable in two ways. First, it does not require the use of human coders. Second, it places text on a continuum of uniqueness rather than dichotomizes it as boiler plate or not.

>>>>

In this approach we follow the common intuition in natural language processing that the informativeness of text is inversely related to the frequency with which that text occurs \citep{robertson2004understanding} (see, e.g., the regular application of term frequency--inverse document frequency (tf-idf) to pre- or post-process text-based datasets and results). Though we cannot speak to whether or not our approach is ultimately better than that taken by \citet{wilkerson2015tracing}, in which they train a classifier to recognize and exclude boilerplate text based on human-labeled data, we note three relative strengths of our approach. First, we do not rely on the development and implementation of a human coding scheme, which is costly and always exhibits some degree of coding error. Second, our approach results in a continuous measure of the information content of text rather than a dichotomous classification of boilerplate or not. Third, and related to the first strength, our approach assigns an informativeness score to all word types, whereas reliance on human classifiers necessarily limits the boilerplate contributions of word types to the word types that were included in the ground truth labeled set.  All this said, dealing with boilerplate/procedural text is an exciting open area of methodological inquiry for quantitative text-as-data research that is focused on legislation.
